 

### 2021-01-26 doc/manuscript/tables_figures/tables.Rmd
update schematic summary with new figure from @rudeboybert

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
options(knitr.table.format = "latex")
```

@@

\newpage

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv(file = "hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)

#add footnote markers:
hypothesis_table[8,2] <- paste0(hypothesis_table[8,2], footnote_marker_number(1)) 
hypothesis_table[8,3] <- paste0(hypothesis_table[8,3], footnote_marker_number(2)) 
hypothesis_table[8,5] <- paste0(hypothesis_table[8,5], footnote_marker_number(3))

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard Forest"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) %>%

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; one had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "One of the two species was negatively correlated with April $T_{max}$, and the other positively correlated with May $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```

>>>>

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
options(knitr.table.format = "latex")
```
(a)

![](schematic_v2.png)

(b)

@@
